---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# ggsdt

<!-- badges: start -->
[![R-CMD-check](https://github.com/kiyomiyoshi/ggsdt/workflows/R-CMD-check/badge.svg)](https://github.com/kiyomiyoshi/ggsdt/actions)
<!-- badges: end -->

The `ggsdt` package implements generalized gaussian signal detection theory analysis (https://doi.org/10.1101/2022.10.28.514329).

## Installation

You can install the development version of `ggsdt` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kiyomiyoshi/ggsdt")
```

## Functions
`fit_ggsdt()`: implements model fitting  
`ggdistr()`: plots internal distributions  
`ggroc1()`: plots type1 ROC  
`ggzroc1()`: plots z-transformed type1 ROC

Consult each function's document for more information: e.g. `help(fit_ggsdt)`

## Example

The `fit_ggsdt()` function requires arguments as specified in Maniscalco & Law’s webpage: <http://www.columbia.edu/~bsm2105/type2sdt/>  
The same arguments are also employed in `metaSDT` package: <https://github.com/craddm/metaSDT>

`nR_S1` and `nR_S2` are response frequency vectors for S1 and S2 stimuli, ordered from highest confidence S1 to highest confidence S2 responses.  
`add_constant = TRUE` adds a small value to the response frequency vectors primarily for avoiding zero-cell-related issues (default value is TRUE). See above pages for more information.

```{r example}
library(ggsdt)

nR_S1 <- c(170, 120, 50, 25, 45, 40)
nR_S2 <- c(40, 50, 30, 20, 70, 240)

f1 <- fit_ggsdt(nR_S1, nR_S2, add_constant = FALSE)
f1
```

```{r fig.height = 2.5, fig.width = 2.5, dpi = 500, message = F, warning = F}
ggdistr(f1[1, 1], f1[1, 2], f1[1, 3])
ggroc1(f1[1, 1], f1[1, 2], f1[1, 3])
ggzroc1(f1[1, 1], f1[1, 2], f1[1, 3])
```
