---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# ggsdt

<!-- badges: start -->
<!-- badges: end -->

The `ggsdt` package implements generalized gaussian signal detection theory analysis.

## Installation

You can install the development version of `ggsdt` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kiyomiyoshi/ggsdt")
```
## Example

The `fit_ggsdt` function requires arguments as specified in Maniscalco & Law’s webpage: <http://www.columbia.edu/~bsm2105/type2sdt/>

The same arguments are also employed in `metaSDT` package: <https://github.com/craddm/metaSDT>

nR_S1 and nR_S2 are response frequency vectors, ordered from highest confidence S2 to highest confidence S1.

add_constant = T adds a small value to the response frequency vectors primarily for avoiding zero-cell-related issues (see above pages).

```{r example}
library(ggsdt)

nR_S1 <- c(40, 45, 25, 50, 120, 170) # response frequency for S1 stimuli
nR_S2 <- c(240, 70, 20, 30, 50, 40)  # response frequency for S2 stimuli

f1 <- fit_ggsdt(nR_S1, nR_S2, add_constant = F)
f1
```

```{r fig.height = 2.5, fig.width = 2.5, dpi = 500, message = F, warning = F}
ggdistr(f1[1, 1], f1[1, 2], f1[1, 3])
ggroc1(f1[1, 1], f1[1, 2], f1[1, 3])
ggzroc1(f1[1, 1], f1[1, 2], f1[1, 3])
```
